Open archaeology, open source?

### 2024-02-06 analysis/_03-data_methodology.qmd
Remove filter
None of the items it filters are in open-archaeo any more

```{r data-oarch-filter}
oarch_filter <- read_csv(here("analysis/data/raw_data/open-archaeo_filter.csv"))
n_items_removed <- nrow(filter(oarch_filter, !item_name %in% oarch$item_name))
oarch |>
  filter(!item_name %in% oarch_filter$item_name) ->
  oarch

# Exclude from GitHub API data collection because they part of a larger
# repository (or forked from one)
oarch$gh_repo[oarch$item_name == "ArchaeoLines"] <- NA
oarch$gh_repo[oarch$gh_repo == "carpentries-incubator/R-archaeology-lesson"] <- NA
```

>>>>

```{r data-oarch-filter}
# Exclude from GitHub API data collection because they part of a larger
# repository (or forked from one)
oarch$gh_repo[oarch$item_name == "ArchaeoLines"] <- NA
oarch$gh_repo[oarch$gh_repo == "carpentries-incubator/R-archaeology-lesson"] <- NA
```
